### 2023-02-09 paper/paper.qmd
Start on finalizing paper

---
title: "Searching for Software in NSF Awards"
author:
  - name: "Eva Maxfield Brown"
    orcid: 0000-0003-2564-0373
    affliations:
      - name: University of Washington Information School
  - name: "Lindsey Schwartz"
    orcid: XXXX-XXXX-XXXX-XXXX
    affliations:
      - name: University of Washington Information School
  - name: "Richard Lewei Huang"
    orcid: XXXX-XXXX-XXXX-XXXX
    affliations:
      - name: University of Washington Information School
  - name: "Nicholas Weber"
    orcid: XXXX-XXXX-XXXX-XXXX
    email: nmweber@uw.edu
    affliations:
      - name: University of Washington Information School

abstract: "Some abstract!"

# Styling
# See Quarto docs for more details on styling
# This link is for styling options specific to HTML outputs
# https://quarto.org/docs/reference/formats/html.html

## Basics
bibliography: support/main.bib

## Citation Style Language
# See https://github.com/citation-style-language/styles for more options
# We default to PNAS (Proceedings of the National Academy of Sciences)
csl: support/acm-proceedings.csl

## Specific for target format
format:
  html:
    code-tools: true
    standalone: true
    embed-resources: true
    toc: true
    toc-location: left
    reference-location: margin
    citation-location: margin

execute:
  echo: false
---

## Introduction

Some content!

## Data Collection

### Finding Software Produced by NSF Awards

The first step in our data collection process was to find software outputs from National Science Foundation (NSF) funded research. Our first attempt at finding such software outputs was to search for references and promises of software production within NSF award abstracts, project outcome reports, and papers supported by each award. This initial search process had two main problems: it was time consuming to conduct and it was difficult to verify claims of software production.

```{python}
#| code-fold: true
#| warning: false

from soft_search.data.soft_search_2022 import load_github_repos_with_nsf_refs_2022
from IPython.display import Markdown

github_repos_with_nsf_refs = load_github_repos_with_nsf_refs_2022()
github_query_terms = github_repos_with_nsf_refs["query"].unique()
github_query_terms_str = ""
for i, term in enumerate(github_query_terms):
  if i == 0:
    github_query_terms_str = f"'{term}'"
  elif i < len(github_query_terms) - 1:
    github_query_terms_str = f"{github_query_terms_str}, '{term}'"
  else:
    github_query_terms_str = f"{github_query_terms_str}, or '{term}'"

Markdown(
  f"Our solution to these issues was to instead create a Python script which used "
  f"the GitHub API to search for repositories which included reference to financial "
  f"support from an NSF award in the repositories README.md file. Specifically "
  f"our script queried for README.md files which contained any of the following "
  f"text snippets: {github_query_terms_str}. "
  f"GitHub was selected as the basis for our search because of it's widespread "
  f"adoption and mention in scholarly publication "
  f"[@riseofgithubinscholarlypublication]. "
  f"This search found {len(github_repos_with_nsf_refs)} "
  f"unique repositories which contained a reference to the NSF in the repository's "
  f"README.md file."
)
```

### Software Production Annotation

The next step in our data collection process was to annotate each of the GitHub repositories found as either "software" or "not software." In our initial review of the repositories we had collected, we found that the content of repositories ranged from documentation, experimental notes, course materials, collections of one-off scripts written during a research project, to more typical software libraries with installation instructions, testing, and community support and use.

To come to agreement on annotation criteria we conducted multiple rounds of trial coding on samples of the data. Fleiss' kappa was used to determine if there was agreement between our research team on whether ten GitHub repositories contained 'software' or not. On each round of trial coding ten GitHub repositories were randomly selected from our dataset for each member of our research team to annotate independently. When assessing a repository, members of the research team were allowed to use any information in the repository to determine their annotation (i.e. the content of the README.md file, the repository activity, documentation availability, etc.)

```{python}
#| code-fold: true
#| warning: false

from soft_search.data.irr import print_irr_summary_stats
from IPython.display import Markdown

irr_kappa = print_irr_summary_stats(do_print=False)

Markdown(
  f"Our final round of trial coding showed that there was almost perfect agreement "
  f"between the research team (κ={round(irr_kappa, 3)})."
)
```

Our final annotation criteria was generally inclusive of labeling repositories as software, rather there were specific exclusion criteria that resulted in a repository being labeled as "not software". Specifically repositories were labeled as "not software" when a repository primarily consisted of:

1. project documentation or research notes
2. teaching materials for a workshop or course
3. the source code for a project or research lab website
4. collections of scripts specific to the analysis of a single experiment without regard to futher generalizability
5. utility functions for accessing data without providing any additional processing capacity

We then annotated all GitHub repositories in our dataset as either "software" or "not software" according to our agreed upon annotation criteria.

### Linking GitHub Repositories to NSF Awards

Our final step in data collection was to link the annotated GitHub repositories back to specific NSF awards. To do so, we created a script which would load the webpage for each GitHub repository, scrape the content of the README and find the specific NSF award ID number(s) referenced. While annotating the dataset, and with this script, our dataset size was reduced as we found some repositories were returned in the initial search because of the "NSF" acronym being used by other, non-United-States governmental agencies which also fund research.

When processing each repository, our Python script would load the README content, search for NSF Award ID patterns with regular expressions, and then verify that each NSF award ID found was a valid NSF award ID by requesting metadata for the award from the NSF award API.

```{python}
#| code-fold: true
#| warning: false

from soft_search.data import load_soft_search_2022
from soft_search.data.soft_search_2022 import SoftSearch2022DatasetFields
from soft_search.constants import PredictionLabels
from IPython.display import Markdown

soft_search_2022 = load_soft_search_2022()
num_awards_produced_software = len(
  soft_search_2022[
    soft_search_2022[SoftSearch2022DatasetFields.label] == (
      PredictionLabels.SoftwarePredicted
    )
  ]
)
num_awards_did_not_produce_software = len(
  soft_search_2022[
    soft_search_2022[SoftSearch2022DatasetFields.label] == (
      PredictionLabels.SoftwareNotPredicted
    )
  ]
)

Markdown(
  f"During this NSF award ID validation process we additionally completed the "
  f"final step for constructing our dataset which was to request the text for "
  f"the award's abstract and project outcomes report. This was the final step "
  f"of our data collection process and allowed us to create a dataset of "
  f"{num_awards_produced_software} unique NSF awards labeled as 'produced software' "
  f"and {num_awards_did_not_produce_software} unique NSF awards labeled as "
  f"'did not produce software'."
)
```

## Predictive Models

We trained multiple predictive models using different model architectures and using the two different predictive sources available (the award's abstract text or project outcomes report text). As not all awards in our set had concluded their research, the models trained on the project outcomes report text used a reduced size dataset.

We trained three different models for each of the predictive sources and include a custom regular expression as a baseline for comparison. The models trained include a TF-IDF Word Embedding Logistic Regression model, a Semantic Embedding Logistic Regression model, and a Fine-tuned Transformer model.

```{python}
#| code-fold: true
#| warning: false
#| echo: false
#| output: false

from soft_search.label.model_selection import fit_and_eval_all_models

model_results = fit_and_eval_all_models(train_transformer=False)
```

```{python}
#| code-fold: true
#| warning: false
#| label: tbl-models-from-abstract
#| tbl-cap: Model Results from Training using Abstract Text

model_results[model_results["predictive_source"] == "abstract-text"].reset_index(drop=True)
```

```{python}
#| code-fold: true
#| warning: false
#| label: tbl-models-from-project-outcomes
#| tbl-cap: Model Results from Training using Project Outcomes Reports Text

model_results[model_results["predictive_source"] == "project-outcomes"].reset_index(drop=True)
```

## The NSF-Soft-Search Dataset

The dataset, including our software prediction values is available via a link on our GitHub README.

### Trends and Observations

## Discussion

Our initial method for attempting to find research software was to first use data from the NSF API then look through the abstracts, project outcomes reports, and any attached papers to find references to code repositories. However as this proved to be such a manual and time consuming process we decided against it. While attempting to use this NSF first method to create the dataset, we found that many awards and papers that reference computational methods still do not provide a reference web link to their code repositories or websites. In some cases we manually found repositories related to an award or paper by manual search ourselves. While we support including references to code repositories in award abstracts, outcomes reports, and papers, future research should be conducted on how to enable reconnection of papers with code.

As our dataset was entirely composed of NSF awards which ultimately released or hosted software on GitHub, it is possible that our models learned not to predict if an NSF award would produce software, but rather, if an NSF award would produce “software hosted on GitHub.”

## Acknowledgements

::: {.content-visible unless-format="html"}
## References
:::

### 2023-02-09 soft_search/data/irr.py

@@ -71,7 +71,9 @@ def calc_fleiss_kappa(
     return fleiss_kappa(agg_raters)
 
 
-def print_irr_summary_stats() -> None:
+def print_irr_summary_stats(  # noqa: C901
+    do_print: bool = True,
+) -> float:
     """
     Print useful statistics and summary stats using the stored
     inter-rater reliability data.
@@ -80,6 +82,17 @@ def print_irr_summary_stats() -> None:
     * Cohen's Kappa Statistic for each potential model
     * Mean number of examples for each label between the two annotators
     * The rows which differ between the two annotators
+
+    Parameters
+    ----------
+    do_print: bool
+        Should this function actually print the table
+        Default: True (yes, print the table)
+
+    Returns
+    -------
+    float
+        The overall Fliess Kappa statistic.
     """
     # Load IRR data
     data = load_soft_search_2022_irr()
@@ -131,30 +144,33 @@ def print_irr_summary_stats() -> None:
     )
 
     # Print stats
-    print("Inter-Rater Reliability Statistics and Data Summary:")
-    print("=" * 80)
-    annotator_pairs = combinations(
-        sorted_data[SoftSearch2022IRRDatasetFields.annotator].unique(), 2
-    )
-
-    # Run print
-    print(
-        f"{SoftSearch2022IRRDatasetFields.include_in_definition}: "
-        f"{kappa} ({_iterrpreted_score(kappa)})"
-    )
-    print()
-
-    # Get all possible diffs then drop duplicates
-    diffs = []
-    for anno_one, anno_two in annotator_pairs:
-        diffs.append(
-            annotations_df.loc[annotations_df[anno_one] != annotations_df[anno_two]]
+    if do_print:
+        print("Inter-Rater Reliability Statistics and Data Summary:")
+        print("=" * 80)
+        annotator_pairs = combinations(
+            sorted_data[SoftSearch2022IRRDatasetFields.annotator].unique(), 2
         )
-    diff_df = pd.concat(diffs)
-    diff_df = diff_df.drop_duplicates(subset=["github_link"]).reset_index()
 
-    print("Differing Labels:")
-    print(diff_df)
-    print()
-    print("-" * 80)
-    diff_df.to_csv("irr-diffs.csv", index=False)
+        # Run print
+        print(
+            f"{SoftSearch2022IRRDatasetFields.include_in_definition}: "
+            f"{kappa} ({_iterrpreted_score(kappa)})"
+        )
+        print()
+
[…]

### 2023-02-09 paper/paper.qmd
Tiny bit more work on paper (models section)

@@
 from soft_search.data.irr import print_irr_summary_stats
-from IPython.display import Markdown
 
@@
 from soft_search.constants import PredictionLabels
-from IPython.display import Markdown
 
@@
 
-We trained multiple predictive models using different model architectures and using the two different predictive sources available (the award's abstract text or project outcomes report text).
-As not all awards in our set had concluded their research, the models trained on the project outcomes report text used a reduced size dataset.
-
-We trained three different models for each of the predictive sources and include a custom regular expression as a baseline for comparison.
-The models trained include a TF-IDF Word Embedding Logistic Regression model, a Semantic Embedding Logistic Regression model, and a Fine-tuned Transformer model.
+We trained three different models using the text from either the award abstract or project outcomes report.
+The models trained include a logistic regression model trained with TF-IDF word embeddings (`tfidf-logit`), a logistic regression model trained with semantic embeddings (`semantic-logit`), and a fine-tuned transformer (`fine-tuned-transformer`).
+The semantic embeddings and the base model from which we fine-tuned our own transformer model was the `distilbert-base-uncased-finetuned-sst-2-english` model [@hf_canonical_model_maintainers_2022].
+Additionally, we evaluated a regular expression which matched on common terms relating to software as a baseline.
 
@@
 
-model_results = fit_and_eval_all_models(train_transformer=False)
+model_results = fit_and_eval_all_models()
 ```
@@
 #| warning: false
-#| label: tbl-models-from-abstract
-#| tbl-cap: Model Results from Training using Abstract Text
+#| label: tbl-model-results-from-abstract
+#| tbl-cap: Predictive Model Results (Trained with Abstract Text)
 
-model_results[model_results["predictive_source"] == "abstract-text"].reset_index(drop=True)
+from_abstract = model_results[
+  model_results["predictive_source"] == "abstract-text"
+].reset_index(drop=True)
+
+from_abstract
+```
+
+```{python}
+
+best_model_from_abstract = from_abstract.iloc[0]
+best_model_from_abstract_name = best_model_from_abstract["model"]
+best_model_from_abstract_f1 = best_model_from_abstract["f1"]
+
+Markdown(
+  f"@tbl-model-results-from-abstract reports the results from training using "
+  f"the abstract text as input. The best performing model was the "
+  f"`{best_model_from_abstract_name}` which achieved an F1 of "
+  f"{round(best_model_from_abstract_f1, 3)}."
+)
 ```
@@
 #| warning: false
-#| label: tbl-models-from-project-outcomes
-#| tbl-cap: Model Results from Training using Project Outcomes Reports Text
+#| label: tbl-model-results-from-project-outcomes
+#| tbl-cap: Predictive Model Results (Trained with Project Outcomes Report Text)
 
-model_results[model_results["predictive_source"] == "project-outcomes"].reset_index(drop=True)
+from_po = model_results[
+  model_results["predictive_source"] == "project-outcomes"
+].reset_index(drop=True)
+
+from_po
+```
+
+```{python}
+
+best_model_from_po = from_po.iloc[0]
+best_model_from_po_name = best_model_from_po["model"]
+best_model_from_po_f1 = best_model_from_po["f1"]
+
+Markdown(
+  f"@tbl-model-results-from-project-outcomes reports the results from training using "
+  f"the project outcomes reports as input. The best performing model was the "
+  f"`{best_model_from_po_name}` which achieved an F1 of "
+  f"{round(best_model_from_po_f1, 3)}."
+)
 ```

### 2023-02-10 paper/paper.qmd
More paper progress and EDA section start

@@
 
-## Data Collection
+## Data Collection and Annotation {#sec-data-collection}
 
-### Finding Software Produced by NSF Awards
+### Finding Software Produced by NSF Awards {#sec-finding-soft}
 
@@
   f"Our final round of trial coding showed that there was almost perfect agreement "
-  f"between the research team (κ={round(irr_kappa, 3)})."
+  f"between the research team (K={round(irr_kappa, 3)})."
 )
@@
 
-Our final step in data collection was to link the annotated GitHub repositories back to specific NSF awards.
+Our final step in the data collection process was to link the annotated GitHub repositories back to specific NSF awards.
 To do so, we created a script which would load the webpage for each GitHub repository, scrape the content of the README and find the specific NSF award ID number(s) referenced.
@@
 Additionally, we evaluated a regular expression which matched on common terms relating to software as a baseline.
+Each model was trained with 80% of the data.
+We then test each of the models and use F1 to rank each models performance.
 
@@
 
-model_results = fit_and_eval_all_models()
+model_results = fit_and_eval_all_models(train_transformer=False)
 ```
@@
 ```{python}
+#| code-fold: true
+#| warning: false
 
@@
 
+While the models trained with the project outcomes reports were trained with less data, the best model of the group achieved a higher F1 than any of the models trained with the abstracts.
+While we have not investigated further, we believe this to be because the project outcomes reports contain more direct citation of produced software rather than an abstract's promise of software production.
+
+The data used for training, and functions to reproduce these models, are made available via our Python package: [`soft-search`](https://github.com/si2-urssi/eager).
+
 ## The NSF-Soft-Search Dataset
 
-The dataset, including our software prediction values is available via a link on our GitHub README.
+We have compiled the NSF Soft(ware) Search Dataset (`NSF-Soft-Search`).
+The NSF-Soft-Search dataset contains the metadata, abstract text, project outcomes report text, for all NSF awarded projects during the 2010-2023 period.
+The NSF-Soft-Search dataset additionally contains our predictions for software production using both texts respectively.
+
+```{python}
+#| code-fold: true
+#| warning: false
+#| label: tbl-nsf-soft-search-stats
+#| tbl-cap: Composition of the NSF Soft Search Dataset
+
+import pandas as pd
+
+full_dataset = pd.read_parquet("nsf-soft-search-2022.parquet")
+
+# Get descriptive statistics for each major program
+desc_table_rows = []
+for program in full_dataset.majorProgram.unique():
+    subset = full_dataset[full_dataset.majorProgram == program]
+    total_awards_funded = len(subset)
+    will_produce_software = subset[
+      subset.prediction_from_abstract == "software-predicted"
+    ]
+    num_awards_will_produce_software = len(will_produce_software)
+    percent_awards_will_produce = num_awards_will_produce_software / total_awards_funded
+
+    desc_table_rows.append({
+        "Funding Program": program,
+        "# Awards Funded": total_awards_funded,
+        "# Awards 'Produce Software'": num_awards_will_produce_software,
+        "% Awards 'Produce Software'": percent_awards_will_produce,
+    })
+
+desc_table = pd.DataFrame(desc_table_rows).sort_values(
+    by=["# Awards Funded", "% Awards 'Produce Software'"],
+    ascending=False,
+).reset_index(drop=True)
+desc_table
+```
 
@@
 
-## Discussion
+* Trends in software production over time from abstract
+```{python}
+#| code-fold: true
+#| warning: false
 
-Our initial method for attempting to find research software was to first use data from the NSF API then look through the abstracts, project outcomes reports, and any attached papers to find references to code repositories.
-However as this proved to be such a manual and time consuming process we decided against it.
-While attempting to use this NSF first method to create the dataset, we found that many awards and papers that reference computational methods still do not provide a reference web link to their code repositories or websites.
-In some cases we manually found repositories related to an award or paper by manual search ourselves.
+# Create start year, experation year, and award duration columns for downstream
+full_dataset["startYear"] = full_dataset.startDate.apply(lambda d: d.split("/")[-1])
+full_dataset["expYear"] = full_dataset.expDate.apply(lambda d: d.split("/")[-1])
+full_dataset["awardDuration"] = full_dataset.apply(
+  lambda r: int(r.expYear) - int(r.startYear),
+  axis=1,
+)
+
+# Subset the dataset to remove programs which either do not have many awards in total
+# or do not produce awards which result in software production
+high_soft_prog_df = full_dataset[~full_dataset.majorProgram.isin(
+  ["EHR", "SBE", "TIP", "OISE", "OIA"]
+)]
+```
+
+```{python}
+#| code-fold: true
+#| warning: false
+#| label: fig-soft-over-time
+#| fig-cap: Software Production Over Time (Using Predictions from Abstracts)
+
+import seaborn as sns
+import matplotlib.pyplot as plt
+sns.set_context("paper")
+sns.set_theme(
+    style="ticks", rc={"axes.spines.right": False, "axes.spines.top": False}
+)
+sns.set_style("darkgrid", {"grid.color": "#000000", "grid.linestyle": ":"})
+sns.set_palette(
+    [
+        "#ff6a75",  # cherry-red
+        "#0060df",  # ocean-blue
+        "#068989",  # moss-green
+        "#712290",  # purple
+        "#FFA537",  # orange
+        "#FF2A8A",  # pink
+        "#9059FF",  # lavender
+        "#00B3F5",  # light-blue / sky-blue
+        "#005e5e",  # dark blueish green
+        "#C50143",  # dark-red / maroon
+        "#3fe1b0",  # seafoam / mint
+        "#063F96",  # dark-blue / navy-blue
+        "#FFD567",  # banana-yellow
+    ]
+)
+
+# Prep data for plotting software production over time
+soft_produced_over_time_rows = []
+for start_year in high_soft_prog_df.startYear.unique():
+    year_data = high_soft_prog_df[high_soft_prog_df.startYear == start_year]
+    for program_name, award_count in year_data.majorProgram.value_counts().items():
+        program_preds = year_data[
+          year_data.majorProgram == program_name
+        ].prediction_from_abstract.value_counts()
+        try:
+            predicted_count = program_preds.loc["software-predicted"]
+        except KeyError:
+            predicted_count = 0
+
+        soft_produced_over_time_rows.append({
+            "Funding Program": program_name,
+            "Award Start Year": start_year,
+            "% Awards 'Produce Software'": predicted_count / award_count,
+        })
+
+soft_produced_over_time = pd.DataFrame(soft_produced_over_time_rows)
+
+# Plot over time
+sns.barplot(
+    data=soft_produced_over_time,
+    x="Award Start Year",
+    y="% Awards 'Produce Software'",
+    hue="Funding Program",
+    order=[
+        str(i)
+        for i in range(
+            high_soft_prog_df.startYear.astype(int).min(),
+            high_soft_prog_df.startYear.astype(int).max(),
+        )
+    ],
+)
+plt.xticks(rotation=45, ha="right")
+plt.tight_layout()
+```
+
+```{python}
+#| code-fold: true
+#| warning: false
+#| label: fig-soft-over-duration
+#| fig-cap: Software Production Grouped By Award Duration (Using Predictions from Abstracts)
+
+# Prep data for plotting software production over time
+soft_produced_over_duration_rows = []
+for award_duration in high_soft_prog_df.awardDuration.unique():
+    duration_data = high_soft_prog_df[high_soft_prog_df.awardDuration == award_duration]
+    for program_name, award_count in duration_data.majorProgram.value_counts().items():
+        program_preds = duration_data[
+          duration_data.majorProgram == program_name
+        ].prediction_from_abstract.value_counts()
+        try:
+            predicted_count = program_preds.loc["software-predicted"]
+        except KeyError:
+            predicted_count = 0
+
+        soft_produced_over_duration_rows.append({
+            "Funding Program": program_name,
+            "Award Duration (Years)": award_duration,
+            "% Awards 'Produce Software'": predicted_count / award_count,
+        })
+
+soft_produced_over_duration = pd.DataFrame(soft_produced_over_duration_rows)
+
+# Plot over time
+sns.barplot(
+    data=soft_produced_over_duration,
+    x="Award Duration (Years)",
+    y="% Awards 'Produce Software'",
+    hue="Funding Program",
+)
+plt.tight_layout()
+```
+
+* Number of examples that initially were predicted as producing software but didn't over time
+* Number of examples that initially were not predicted to produce software but did over time
+
+## Conclusion
+
+We introduce NSF-Soft-Search, a pair of novel datasets for studying software production from NSF funded projects.
+The NSF-Soft-Search GitHub Annotations dataset is used to train models which aim to predict software production from either the NSF award abstract text or the project outcomes report text.
+We used these models to generate the NSF-Soft-Search Inferred dataset.
+The NSF-Soft-Search Inferred dataset includes project metadata, abstract, project outcomes report, and a predictions of software production for each NSF funded project between 2010 and 2023.
+We hope that NSF-Soft-Search helps further new studies and findings in understanding the role software development plays in scholarly publication.
+
+All datasets and predictive models produced by this work are available from our GitHub repository: [`si2-urssi/eager`](https://github.com/si2-urssi/eager).
+
+### Limitations
+
+As discussed in @sec-data-collection, the NSF-Soft-Search GitHub Annotations dataset was entirely composed of NSF awards which ultimately released or hosted software (and other research products) on GitHub.
+Due to data collection strategy, it is possible that each of the predictive models learned not to predict if an NSF award would produce software, but rather, if an NSF award would produce “software hosted on GitHub.”
+
+### Future Work
+
+As discussed in @sec-finding-soft, our initial method for attempting to find research software produced from NSF supported awards was to search for references and promises of software production in the abstract, project outcomes report, and attached papers of each award.
+While attempting this approach to create the dataset, we found that many awards and papers that reference computational methods do not provide a reference web link to their code repositories or websites.
+In some cases, we found repositories related to an award or paper via Google and GitHub search ourselves.
 While we support including references to code repositories in award abstracts, outcomes reports, and papers, future research should be conducted on how to enable reconnection of papers with code.
 
-As our dataset was entirely composed of NSF awards which ultimately released or hosted software on GitHub, it is possible that our models learned not to predict if an NSF award would produce software, but rather, if an NSF award would produce “software hosted on GitHub.”
+## Acknowledgements
 
-## Acknowledgements
+We wish to thank ....
+
+This work was supported in part by NSF Grant
 

### 2023-02-10 soft_search/bin/generate_nsf_soft_search_2022_dataset.py

@@ -11,7 +11,11 @@ import pandas as pd
 from tqdm import tqdm
 
 from soft_search import nsf
-from soft_search.constants import ALL_NSF_PROGRAMS
+from soft_search.constants import ALL_NSF_PROGRAMS, NSFFields
+from soft_search.label import (
+    load_tfidf_logit_for_prediction_from_abstract,
+    load_tfidf_logit_for_prediction_from_outcomes,
+)
 
 ###############################################################################
 
@@ -22,17 +26,18 @@ class Args(argparse.Namespace):
 
     def __parse(self) -> None:
         p = argparse.ArgumentParser(
-            prog="get-nsf-award-set-for-soft-search-2022",
+            prog="generate-nsf-soft-search-2022-dataset",
             description=(
-                "Get the NSF awards dataset for use in "
-                "downstream prediction of software."
+                "Get the NSF Awards from the last 12 years, predict "
+                "if they produced software from both the abstract and the "
+                "project outcomes report and archive the results."
             ),
         )
         p.add_argument(
             "-s",
             "--start-date",
             dest="start_date",
-            default="2016-01-01",
+            default="2010-01-01",
             type=str,
             help="ISO format string with the date to start gathering awards for.",
         )
@@ -48,7 +53,7 @@ class Args(argparse.Namespace):
             "-o",
             "--outfile",
             dest="outfile",
-            default=Path("./soft-search-awards.csv"),
+            default=Path("./nsf-soft-search-2022.csv"),
             type=Path,
             help="The path to store the dataset CSV (and Parquet with the same name).",
         )
@@ -101,10 +106,31 @@ def main() -> None:
         # Concat and report size
         awards = (
             pd.concat(program_chunks, ignore_index=True)
-            .drop_duplicates("id")
+            .drop_duplicates(NSFFields.id_)
+            .dropna(subset=[NSFFields.abstractText])
             .reset_index(drop=True)
         )
         log.info(f"Total awards found: {len(awards)}")
+
+        # Make predictions
+        log.info("Loading model and predicting software production from abstract.")
+        model = load_tfidf_logit_for_prediction_from_abstract()
+        awards["prediction_from_abstract"] = model.predict(
+            awards[NSFFields.abstractText],
+        )
+
+        log.info("Loading model and predicting software production from outcomes.")
+        model = load_tfidf_logit_for_prediction_from_outcomes()
+
[…]

### 2023-02-10 soft_search/nsf.py

@@ -7,7 +7,12 @@ import pandas as pd
 import requests
 from tqdm import tqdm
 
-from .constants import ALL_NSF_FIELDS, NSF_PROGRAM_TO_CFDA_NUMBER_LUT, NSFPrograms
+from .constants import (
+    ALL_NSF_FIELDS,
+    NSF_PROGRAM_TO_CFDA_NUMBER_LUT,
+    NSFFields,
+    NSFPrograms,
+)
 
 ###############################################################################
 # Constants
@@ -204,6 +209,6 @@ def get_nsf_dataset(
     # Concat all awards
     return (
         pd.concat(chunks, ignore_index=True)
-        .drop_duplicates("id")
+        .drop_duplicates(NSFFields.id_)
         .reset_index(drop=True)
     )

### 2023-02-10 paper/paper.qmd
Introduction done

@@
 
+## Number sections (required for section cross ref)
+number-sections: true
+
 ## Citation Style Language
@@
 
-## Introduction
+# Introduction
 
-Some content!
+Software production, use, and reuse is an increasingly crucial part of scholarly work [@open_source_code_repo_predict_impact;@Trisovic2021ALS].
+While historically ignored, citing and referencing software used during the course of research is becoming common with new standards for software citation [@Katz2021RecognizingTV;@Du2022UnderstandingPI] and work in extracting software references in existing literature [@cz_software_mentions].
+However, records of software production are not available at scale the way other bibliographic metrics are.
+To solve this problem, we introduce two related datasets for studying and inferring software produced as a part of research, which we refer to as the NSF-Soft-Search dataset.
 
-## Data Collection and Annotation {#sec-data-collection}
+The NSF-Soft-Search dataset is aimed at identifying research projects which are likely to have produced software during the course of a project.
+We start by identifying GitHub repositories which acknowledge funding from at least one National Science Foundation (NSF) award.
+We then annotate each GitHub repository found with a binary decision for it's contents: software or not-software (research notes, course materials, etc.).
+We link each annotated GitHub repository to the specific NSF award ID(s) referenced in it's README.md file.
+Finally, we compile the NSF-Soft-Search GitHub Annotations dataset using the annotations for each GitHub repository, and the text from the linked NSF award abstract and the project outcomes report.
 
-### Finding Software Produced by NSF Awards {#sec-finding-soft}
+Using the NSF-Soft-Search GitHub Annotations dataset, we train a variety of models which aim to predict software production using either the NSF award abstract or project outcomes report text as input.
+We use the best performing models to then infer software production against all awards funded by the National Science Foundation from 2010 to 2023.
+The predictions and metadata for each NSF award between the 2010 and 2023 period are compiled to form the NSF-Soft-Search Inferred dataset.
+
+The rest of the paper proceeds as follows.
+In @sec-data-collection we detail the data collection and annotation process used for creating the NSF-Soft-Search GitHub Annotations dataset.
+In @sec-models we briefly describe the model training process and report results for the all of the models trained.
+In @sec-nsf-soft-search-dataset we provide summary statistics for the NSF-Soft-Search Inferred dataset and use the dataset to observe trends in software production over time.
+We conclude with discussion regarding the limitations of our approach and opportunities for future work.
+
+# Data Collection and Annotation {#sec-data-collection}
+
+## Finding Software Produced by NSF Awards {#sec-finding-soft}
 
@@
 
-### Software Production Annotation
+## Software Production Annotation
 
@@
 
-### Linking GitHub Repositories to NSF Awards
+## Linking GitHub Repositories to NSF Awards
 
@@
 
-## Predictive Models
+# Predictive Models {#sec-models}
 
@@
 
-from_abstract
+Markdown(from_abstract.to_markdown(index=False))
 ```
@@
 
-from_po
+Markdown(from_po.to_markdown(index=False))
 ```
@@
 
-## The NSF-Soft-Search Dataset
+# The NSF-Soft-Search Dataset {#sec-nsf-soft-search-dataset}
 
@@
         "# Awards Funded": total_awards_funded,
-        "# Awards 'Produce Software'": num_awards_will_produce_software,
-        "% Awards 'Produce Software'": percent_awards_will_produce,
+        "# 'Produce Software'": num_awards_will_produce_software,
+        "% 'Produce Software'": percent_awards_will_produce,
     })
@@
 desc_table = pd.DataFrame(desc_table_rows).sort_values(
-    by=["# Awards Funded", "% Awards 'Produce Software'"],
+    by=["# Awards Funded", "% 'Produce Software'"],
     ascending=False,
 ).reset_index(drop=True)
-desc_table
+Markdown(desc_table.to_markdown(index=False))
 ```
 
-### Trends and Observations
+## Trends and Observations
 
-* Trends in software production over time from abstract
 ```{python}
@@
             "Award Start Year": start_year,
-            "% Awards 'Produce Software'": predicted_count / award_count,
+            "% 'Produce Software'": predicted_count / award_count,
         })
@@
 
+# Ensure that hue colors are consistent throughout plots
+soft_produced_over_time = soft_produced_over_time.sort_values(
+  by="Funding Program",
+)
+
 # Plot over time
-sns.barplot(
+ax = sns.barplot(
     data=soft_produced_over_time,
     x="Award Start Year",
-    y="% Awards 'Produce Software'",
+    y="% 'Produce Software'",
     hue="Funding Program",
@@
     ],
+)
+sns.move_legend(
+    ax,
+    "lower center",
+    bbox_to_anchor=(.5, 1),
+    ncol=len(soft_produced_over_time["Funding Program"].unique()),
+    title="Funding Program",
+    frameon=False,
 )
@@
             "Award Duration (Years)": award_duration,
-            "% Awards 'Produce Software'": predicted_count / award_count,
+            "% 'Produce Software'": predicted_count / award_count,
         })
@@
 
+# Ensure that hue colors are consistent throughout plots
+soft_produced_over_duration = soft_produced_over_duration.sort_values(
+  by="Funding Program",
+)
+
 # Plot over time
-sns.barplot(
+ax = sns.barplot(
     data=soft_produced_over_duration,
     x="Award Duration (Years)",
-    y="% Awards 'Produce Software'",
+    y="% 'Produce Software'",
     hue="Funding Program",
+)
+sns.move_legend(
+    ax,
+    "lower center",
+    bbox_to_anchor=(.5, 1),
+    ncol=len(soft_produced_over_time["Funding Program"].unique()),
+    title="Funding Program",
+    frameon=False,
 )
@@
 
-## Conclusion
+# Conclusion
 
@@
 We used these models to generate the NSF-Soft-Search Inferred dataset.
-The NSF-Soft-Search Inferred dataset includes project metadata, abstract, project outcomes report, and a predictions of software production for each NSF funded project between 2010 and 2023.
+The NSF-Soft-Search Inferred dataset includes project metadata, abstract, project outcomes report, and predictions of software production for each NSF funded project between 2010 and 2023.
 We hope that NSF-Soft-Search helps further new studies and findings in understanding the role software development plays in scholarly publication.
@@
 
-### Limitations
+## Limitations
 
@@
 
-### Future Work
+## Future Work
 
@@
 
-## Acknowledgements
+# Acknowledgements
 
@@
 ::: {.content-visible unless-format="html"}
-## References
+# References
 :::

### 2023-02-10 soft_search/nsf.py

@@ -78,7 +78,11 @@ def _get_nsf_chunk(
     )
 
     # Parse and return
-    return pd.DataFrame(response.json()["response"]["award"])
+    response_json = response.json()["response"]
+    if "award" in response_json:
+        return pd.DataFrame(response_json["award"])
+    
+    return pd.DataFrame()
 
 
 def get_nsf_dataset(

### 2023-02-10 paper/paper.qmd
Minor paper updates

@@
 
-abstract: "Some abstract!"
+abstract: |
+  Software production, use, and reuse is a crucial part of scholarly work but software products of research are in many cases not easily identifiable or discoverable.
+The first step of automatic linkage of research and software is identification.
+In this paper we present two datasets to study the identification and production of research software.
+The first dataset contains almost 1000 annotations of software production from National Science Foundation (NSF) awarded research projects.
+We use this dataset to train models which predict software production from either the text of an NSF award's abstract or project outcomes report.
+Our second dataset is created by applying the trained predictive models across the abstracts and project outcomes reports for all NSF funded projects between the years of 2010 and 2023.
+The result is an inferred dataset of software production for over XXXXX NSF awards.
+We release the NSF-Soft-Search dataset to aid in identifying and understanding research software production: https://github.com/si2-urssi/eager
 
@@
 In some cases, we found repositories related to an award or paper via Google and GitHub search ourselves.
-While we support including references to code repositories in award abstracts, outcomes reports, and papers, future research should be conducted on how to enable reconnection of papers with code.
+While we support including references to code repositories in award abstracts, outcomes reports, and papers, future research should be conducted on how to enable automatic reconnection of papers and their software outputs.
 
@@
 
-This work was supported in part by NSF Grant
+This work was supported in part by NSF Grant ####
 

### 2023-02-10 paper/paper.qmd
Last 9 page paper push
Use ACM template for paper

@@
   - name: "Eva Maxfield Brown"
+    email: evamxb@uw.edu
     orcid: 0000-0003-2564-0373
-    affliations:
-      - name: University of Washington Information School
+    affliation:
+        name: University of Washington Information School
+        city: Seattle
+        state: Washington
+        country: USA
   - name: "Lindsey Schwartz"
-    orcid: XXXX-XXXX-XXXX-XXXX
-    affliations:
-      - name: University of Washington Information School
+    email: lsschwar@uw.edu
+    affliation:
+        name: University of Washington Information School
+        city: Seattle
+        state: Washington
+        country: USA
   - name: "Richard Lewei Huang"
-    orcid: XXXX-XXXX-XXXX-XXXX
-    affliations:
-      - name: University of Washington Information School
+    email: lwhuang@uw.edu
+    affliation:
+        name: University of Washington Information School
+        city: Seattle
+        state: Washington
+        country: USA
   - name: "Nicholas Weber"
-    orcid: XXXX-XXXX-XXXX-XXXX
     email: nmweber@uw.edu
-    affliations:
-      - name: University of Washington Information School
+    orcid: 0000-0002-6008-3763
+    affliation:
+        name: University of Washington Information School
+        city: Seattle
+        state: Washington
+        country: USA
 
@@
 Our second dataset is created by applying the trained predictive models across the abstracts and project outcomes reports for all NSF funded projects between the years of 2010 and 2023.
-The result is an inferred dataset of software production for over XXXXX NSF awards.
+The result is an inferred dataset of software production for over 150,000 NSF awards.
 We release the NSF-Soft-Search dataset to aid in identifying and understanding research software production: https://github.com/si2-urssi/eager
@@
   echo: false
+
+keep-tex: true
+keep-ipynb: true
+
+# acm-specific metadata
+acm-metadata:
+  # comment this out to make submission anonymous
+  anonymous: true
+
+  # comment this out to build a draft version
+  # final: true
+
+  # comment this out to specify detailed document options
+  acmart-options: sigconf, review
+
+  # acm preamble information
+  copyright-year: 2023
+  acm-year: 2023
+  copyright: acmcopyright
+  doi: XXXXXXX.XXXXXXX
+  conference-acronym: JCDL
+  conference-name: Joint Conference on Digital Libraries
+  conference-date: June 26--30, 2023
+  conference-location: Santa Fe, NM
+  # price: "15.00"
+  # isbn: 978-1-4503-XXXX-X/18/06
+
+  # if present, replaces the list of authors in the page header.
+  shortauthors: Brown et al.
+
+  keywords:
+    - datasets
+    - text classification
+    - research software
 ---
@@
 ].reset_index(drop=True)
-
-Markdown(from_abstract.to_markdown(index=False))
+from_abstract.loc[:, from_abstract.columns != "predictive_source"]
 ```
@@
 ].reset_index(drop=True)
-
-Markdown(from_po.to_markdown(index=False))
+from_po.loc[:, from_po.columns != "predictive_source"]
 ```
@@
     desc_table_rows.append({
-        "Funding Program": program,
-        "# Awards Funded": total_awards_funded,
-        "# 'Produce Software'": num_awards_will_produce_software,
-        "% 'Produce Software'": percent_awards_will_produce,
+        "Program": program,
+        "# Awards": total_awards_funded,
+        "# Software": num_awards_will_produce_software,
+        "% Software": percent_awards_will_produce,
     })
@@
 desc_table = pd.DataFrame(desc_table_rows).sort_values(
-    by=["# Awards Funded", "% 'Produce Software'"],
+    by=["# Awards", "% Software"],
     ascending=False,
 ).reset_index(drop=True)
-Markdown(desc_table.to_markdown(index=False))
+desc_table
 ```
@@
         soft_produced_over_time_rows.append({
-            "Funding Program": program_name,
+            "Program": program_name,
             "Award Start Year": start_year,
@@
 soft_produced_over_time = soft_produced_over_time.sort_values(
-  by="Funding Program",
+  by="Program",
 )
@@
     y="% 'Produce Software'",
-    hue="Funding Program",
+    hue="Program",
     order=[
         str(i)
-        for i in range(
-            high_soft_prog_df.startYear.astype(int).min(),
-            high_soft_prog_df.startYear.astype(int).max(),
-        )
+        for i in range(2010, 2023)
     ],
@@
     bbox_to_anchor=(.5, 1),
-    ncol=len(soft_produced_over_time["Funding Program"].unique()),
-    title="Funding Program",
+    ncol=len(soft_produced_over_time["Program"].unique()),
+    title="Program",
     frameon=False,
@@
 ```
+
+Using the NSF-Soft-Search Inferred dataset we can observe trends in software production over time.
+@fig-soft-over-time plots the percent of awards which we predict to have produced software (using the award's abstract) over time.
+While there are minor deviations year-to-year in predicted software production, we observe the "Math and Physical Sciences" (MPS) funding program as funding the most awards which we predict to produce software, with "Computer and Information Science and Engineering" (CISE), and "Engineering" (ENG) close behind.
 
@@
         soft_produced_over_duration_rows.append({
-            "Funding Program": program_name,
+            "Program": program_name,
             "Award Duration (Years)": award_duration,
@@
 soft_produced_over_duration = soft_produced_over_duration.sort_values(
-  by="Funding Program",
+  by="Program",
 )
+
+# We don't have many awards that are funded for more than 9 years
+# This leads to deceptive plots -- remove greater than 9
+soft_produced_over_duration = soft_produced_over_duration[
+  soft_produced_over_duration["Award Duration (Years)"] <= 9
+]
+
+# Filter out oddities
+soft_produced_over_duration = soft_produced_over_duration[
+  soft_produced_over_duration["Award Duration (Years)"] >= 0
+]
 
@@
     y="% 'Produce Software'",
-    hue="Funding Program",
+    hue="Program",
 )
@@
 
-* Number of examples that initially were predicted as producing software but didn't over time
-* Number of examples that initially were not predicted to produce software but did over time
+We can additionally observe trends in software production as award duration increases.
+@fig-soft-over-duration plots the percent of awards which we predict to have produced software (using the award's abstract) grouped by the award duration in years.
+We note that as award duration increases, the percentage of awards which are predicted to have produced software also tends to increase.
 
@@
 
-::: {.content-visible unless-format="html"}
 # References
-:::

### 2023-02-10 soft_search/bin/generate_nsf_soft_search_2022_dataset.py
Lint and format

@@ -128,7 +128,7 @@ def main() -> None:
             outcomes_awards[NSFFields.projectOutComesReport],
         )
         outcomes_awards = outcomes_awards[[NSFFields.id_, "prediction_from_outcomes"]]
-        
+
         # Join the outcomes predictions back to the full set
         awards = awards.join(outcomes_awards.set_index(NSFFields.id_), on=NSFFields.id_)
 

### 2023-02-10 soft_search/nsf.py

@@ -81,7 +81,7 @@ def _get_nsf_chunk(
     response_json = response.json()["response"]
     if "award" in response_json:
         return pd.DataFrame(response_json["award"])
-    
+
     return pd.DataFrame()
 
 

### 2023-02-14 paper/paper.qmd
Changes from paper draft review

@@
 abstract: |
-  Software production, use, and reuse is a crucial part of scholarly work but software products of research are in many cases not easily identifiable or discoverable.
-The first step of automatic linkage of research and software is identification.
+  Software is an important tool for scholarly work, but software produced for research is in many cases not easily identifiable or discoverable.
+A potential first step in linking research and software is software identification.
 In this paper we present two datasets to study the identification and production of research software.
-The first dataset contains almost 1000 annotations of software production from National Science Foundation (NSF) awarded research projects.
-We use this dataset to train models which predict software production from either the text of an NSF award's abstract or project outcomes report.
+The first dataset contains almost 1000 human labeled annotations of software production from National Science Foundation (NSF) awarded research projects.
+We use this dataset to train models that  predict software production.
 Our second dataset is created by applying the trained predictive models across the abstracts and project outcomes reports for all NSF funded projects between the years of 2010 and 2023.
@@
   # comment this out to build a draft version
-  # final: true
+  final: true
 
@@
 Software production, use, and reuse is an increasingly crucial part of scholarly work [@open_source_code_repo_predict_impact;@Trisovic2021ALS].
-While historically ignored, citing and referencing software used during the course of research is becoming common with new standards for software citation [@Katz2021RecognizingTV;@Du2022UnderstandingPI] and work in extracting software references in existing literature [@cz_software_mentions].
-However, records of software production are not available at scale the way other bibliographic metrics are.
-To solve this problem, we introduce two related datasets for studying and inferring software produced as a part of research, which we refer to as the NSF-Soft-Search dataset.
+While historically underutilized, citing and referencing software used during the course of research is becoming common with new standards for software citation [@Katz2021RecognizingTV;@Du2022UnderstandingPI] and work in extracting software references in existing literature [@cz_software_mentions].
+However, records of software production are not readily identifiable or available at scale in the way that peer-reviewed publications or other scholarly outputs are [@Schindler2022TheRO].
+To make progress on this problem, we introduce two related datasets for studying and inferring software produced as a part of research, which we refer to as the NSF-Soft-Search dataset.
 
-The NSF-Soft-Search dataset is aimed at identifying research projects which are likely to have produced software during the course of a project.
-We start by identifying GitHub repositories which acknowledge funding from at least one National Science Foundation (NSF) award.
-We then annotate each GitHub repository found with a binary decision for it's contents: software or not-software (research notes, course materials, etc.).
-We link each annotated GitHub repository to the specific NSF award ID(s) referenced in it's README.md file.
-Finally, we compile the NSF-Soft-Search GitHub Annotations dataset using the annotations for each GitHub repository, and the text from the linked NSF award abstract and the project outcomes report.
+The NSF-Soft-Search dataset is aimed at identifying research projects which are likely to have produced software while funded by a federal grant.
+We start by identifying GitHub repositories that  acknowledge funding from at least one National Science Foundation (NSF) award.
+We then annotate each GitHub repository found with a binary decision for its contents: software or not-software (e.g.
+not all github repositories contain software, they might include research notes, course materials, etc.).
+We then link each annotated GitHub repository to the specific NSF award ID(s) referenced in its README.md file.
+Finally, we compile the NSF-Soft-Search Training dataset using the annotations for each GitHub repository, and the text from the linked NSF award abstract and the project outcomes report.
 
-Using the NSF-Soft-Search GitHub Annotations dataset, we train a variety of models which aim to predict software production using either the NSF award abstract or project outcomes report text as input.
-We use the best performing models to then infer software production against all awards funded by the National Science Foundation from 2010 to 2023.
+Using the NSF-Soft-Search Training dataset, we train a variety of models to predict software production using either the NSF award abstract or project outcomes report text as input.
+We use the best performing models to then infer software production against all awards funded by the National Science Foundation from 2010 to 2023 (additional details are offered in @sec-data-collection).
 The predictions and metadata for each NSF award between the 2010 and 2023 period are compiled to form the NSF-Soft-Search Inferred dataset.
 
+In total, our new NSF-Soft-Search dataset includes the following contributions:
+
+1. NSF-Soft-Search Training: A ground truth dataset compiled using linked NSF awards and GitHub repositories which have been annotated for software production.
+2. Multiple classifiers which infer software production from either the text of an NSF award’s abstract or project outcomes report.
+3.
+NSF-Soft-Search Inferred: A dataset of more than 150,000 NSF funded awards from between 2010 and 2023.
+Each award has two predictions for software production: one from prediction using the abstract text and the other from prediction using the project outcomes report text.
+
 The rest of the paper proceeds as follows.
-In @sec-data-collection we detail the data collection and annotation process used for creating the NSF-Soft-Search GitHub Annotations dataset.
-In @sec-models we briefly describe the model training process and report results for the all of the models trained.
-In @sec-nsf-soft-search-dataset we provide summary statistics for the NSF-Soft-Search Inferred dataset and use the dataset to observe trends in software production over time.
+In @sec-data-collection we detail the data collection and annotation process used for creating the NSF-Soft-Search Training dataset.
+In @sec-models we briefly describe the model training process and report results.
+In @sec-nsf-soft-search-dataset we provide summary statistics for the NSF-Soft-Search Inferred dataset and observe trends in software production over time.
 We conclude with discussion regarding the limitations of our approach and opportunities for future work.
@@
 The first step in our data collection process was to find software outputs from National Science Foundation (NSF) funded research.
-Our first attempt at finding such software outputs was to search for references and promises of software production within NSF award abstracts, project outcome reports, and papers supported by each award.
-This initial search process had two main problems: it was time consuming to conduct and it was difficult to verify claims of software production.
+This step has two potential approaches.
+The first approach is a manual search for references and promises of software production within NSF award abstracts, project outcome reports, and papers supported by each award.
+This first approach is labor intensive and may be prone to labeling errors because while there may be a promise of software production in these documents, it may not be possible to verify such software was ultimately produced.
+The other approach is to predict software production using a trained model.
+We pursue this approach with the caveat that there are also potential label errors.
 
@@
 Markdown(
-  f"Our solution to these issues was to instead create a Python script which used "
-  f"the GitHub API to search for repositories which included reference to financial "
-  f"support from an NSF award in the repositories README.md file. Specifically "
-  f"our script queried for README.md files which contained any of the following "
-  f"text snippets: {github_query_terms_str}. "
-  f"GitHub was selected as the basis for our search because of it's widespread "
+  f"To gather examples of verifiable software production, we created "
+  f"a Python script which used the GitHub API to search for repositories which "
+  f"included reference to financial support from an NSF award in the "
+  f"repositories README.md file. Specifically our script queried for README.md "
+  f"files which contained any of the following text snippets: "
+  f"{github_query_terms_str}. "
+  f"GitHub was selected as the basis for our search because of its widespread "
   f"adoption and mention in scholarly publication "
@@
 
-To come to agreement on annotation criteria we conducted multiple rounds of trial coding on samples of the data.
+Using existing definitions of what constitutes research software to form the basis of our annotation criteria [@martinez_ortiz_carlos_2022_7185371;@sochat2022research], we conducted multiple rounds of trial coding on samples of the data.
 Fleiss' kappa was used to determine if there was agreement between our research team on whether ten GitHub repositories contained 'software' or not.
@@
 Markdown(
-  f"Our final round of trial coding showed that there was almost perfect agreement "
-  f"between the research team (K={round(irr_kappa, 3)})."
+  f"Our final round of trial coding showed that there was near perfect agreement "
+  f"between the research team (K={round(irr_kappa, 3)}) [@viera2005understanding]."
 )
@@
 3. the source code for a project or research lab website
-4. collections of scripts specific to the analysis of a single experiment without regard to futher generalizability
+4. collections of scripts specific to the analysis of a single experiment without regard to further generalizability
 5. utility functions for accessing data without providing any additional processing capacity
@@
 Our final step in the data collection process was to link the annotated GitHub repositories back to specific NSF awards.
-To do so, we created a script which would load the webpage for each GitHub repository, scrape the content of the README and find the specific NSF award ID number(s) referenced.
-While annotating the dataset, and with this script, our dataset size was reduced as we found some repositories were returned in the initial search because of the "NSF" acronym being used by other, non-United-States governmental agencies which also fund research.
+To do so, we created a script which would load the webpage for each GitHub repository, scrape the content of the repository’s README and find the specific NSF award ID number(s) referenced.
+While annotating the dataset, and with this script, our dataset size was reduced as we found some repositories were returned in the initial search because of the “NSF” acronym being used by other, non-United-States governmental agencies which also fund research.
 
-When processing each repository, our Python script would load the README content, search for NSF Award ID patterns with regular expressions, and then verify that each NSF award ID found was a valid NSF award ID by requesting metadata for the award from the NSF award API.
+When processing each repository, our Python script would load the README content, search for NSF Award ID patterns with regular expressions, and then verify that each NSF award ID found was valid by requesting metadata for the award from the NSF award API.
 
@@
 Markdown(
-  f"During this NSF award ID validation process we additionally completed the "
-  f"final step for constructing our dataset which was to request the text for "
-  f"the award's abstract and project outcomes report. This was the final step "
-  f"of our data collection process and allowed us to create a dataset of "
-  f"{num_awards_produced_software} unique NSF awards labeled as 'produced software' "
-  f"and {num_awards_did_not_produce_software} unique NSF awards labeled as "
-  f"'did not produce software'."
+  f"We then retrieved the text for each award's abstract and project outcomes report. "
+  f"This was the final step of our data collection process and allowed us to create "
+  f"a dataset of {num_awards_produced_software} unique NSF awards labeled as "
+  f"'produced software' and {num_awards_did_not_produce_software} unique NSF awards "
+  f"labeled as 'did not produce software'."
 )
@@
 
-We trained three different models using the text from either the award abstract or project outcomes report.
-The models trained include a logistic regression model trained with TF-IDF word embeddings (`tfidf-logit`), a logistic regression model trained with semantic embeddings (`semantic-logit`), and a fine-tuned transformer (`fine-tuned-transformer`).
+Using the compiled NSF-Soft-Search Training dataset, we trained three different models using the text from either the award abstract or project outcomes report.
+The models trained include a logistic regression model trained with TF-IDF word embeddings (`tfidf-logit`), a logistic regression model trained with semantic embeddings (`semantic-logit`), and a fine-tuned transformer (`transformer`).
 The semantic embeddings and the base model from which we fine-tuned our own transformer model was the `distilbert-base-uncased-finetuned-sst-2-english` model [@hf_canonical_model_maintainers_2022].
-Additionally, we evaluated a regular expression which matched on common terms relating to software as a baseline.
-Each model was trained with 80% of the data.
-We then test each of the models and use F1 to rank each models performance.
+Each model was trained with 80% of the NSF-Soft-Search Training dataset.
+We then test each of the models and use F1 to rank each model’s performance.
 
@@
 
-model_results = fit_and_eval_all_models()
+model_results = fit_and_eval_all_models().round(3)
 ```
@@
 
-We have compiled the NSF Soft(ware) Search Dataset (`NSF-Soft-Search`).
-The NSF-Soft-Search dataset contains the metadata, abstract text, project outcomes report text, for all NSF awarded projects during the 2010-2023 period.
-The NSF-Soft-Search dataset additionally contains our predictions for software production using both texts respectively.
+Using the predictive models, we compile the NSF-Soft-Search Inferred dataset which contains the metadata, abstract text, and project outcomes report text, for all NSF awarded projects during the 2010-2023 period.
+The NSF-Soft-Search Inferred dataset additionally contains our predictions for software production using both texts respectively.
 
@@
 @fig-soft-over-time plots the percent of awards which we predict to have produced software (using the award's abstract) over time.
-While there are minor deviations year-to-year in predicted software production, we observe the "Math and Physical Sciences" (MPS) funding program as funding the most awards which we predict to produce software, with "Computer and Information Science and Engineering" (CISE), and "Engineering" (ENG) close behind.
+While there are minor year-to-year deviations in predicted software production, we observe the "Math and Physical Sciences" (MPS) funding program as funding the most awards which we predict to produce software, with "Computer and Information Science and Engineering" (CISE), and "Engineering" (ENG) close behind.
 
@@
 We introduce NSF-Soft-Search, a pair of novel datasets for studying software production from NSF funded projects.
-The NSF-Soft-Search GitHub Annotations dataset is used to train models which aim to predict software production from either the NSF award abstract text or the project outcomes report text.
+The NSF-Soft-Search Training dataset is a human-labeled dataset with almost 1000 examples used to train models which predict software production from either the NSF award abstract text or the project outcomes report text.
 We used these models to generate the NSF-Soft-Search Inferred dataset.
-The NSF-Soft-Search Inferred dataset includes project metadata, abstract, project outcomes report, and predictions of software production for each NSF funded project between 2010 and 2023.
+The NSF-Soft-Search Inferred dataset includes project metadata, the awards abstract and project outcomes report, and predictions of software production for each NSF funded project between 2010 and 2023.
 We hope that NSF-Soft-Search helps further new studies and findings in understanding the role software development plays in scholarly publication.
@@
 
-As discussed in @sec-data-collection, the NSF-Soft-Search GitHub Annotations dataset was entirely composed of NSF awards which ultimately released or hosted software (and other research products) on GitHub.
-Due to data collection strategy, it is possible that each of the predictive models learned not to predict if an NSF award would produce software, but rather, if an NSF award would produce “software hosted on GitHub.”
+As discussed in @sec-data-collection, the NSF-Soft-Search Training dataset was entirely composed of NSF awards which ultimately released or hosted software (and other research products) on GitHub.
+Due to our data collection strategy, it is possible that each of the predictive models learned not to predict if an NSF award would produce software, but rather, if an NSF award would produce software hosted on GitHub.
 

### 2023-02-14 soft_search/label/transformer.py

@@ -230,7 +230,7 @@ def train(
     epoch_metrics = trainer.train()
     raw_eval_metrics = trainer.evaluate(tokenized_test_dataset)
     eval_metrics = EvaluationMetrics(
-        model="fine-tuned-transformer",
+        model="transformer",
         accuracy=raw_eval_metrics["eval_accuracy"],
         precision=raw_eval_metrics["eval_precision"],
         recall=raw_eval_metrics["eval_recall"],

### 2023-02-14 paper/paper.qmd
Minor styling adjustments to paper

@@
 # We default to PNAS (Proceedings of the National Academy of Sciences)
-csl: support/acm-proceedings.csl
+# csl: support/acm-proceedings.csl
 
@@
   # comment this out to specify detailed document options
-  acmart-options: sigconf, review
+  acmart-options: sigconf
 
@@
     - research software
+
+  ccs: |
+    \begin{CCSXML}
+    <ccs2012>
+      <concept>
+          <concept_id>10002951.10003227.10003392</concept_id>
+          <concept_desc>Information systems~Digital libraries and archives</concept_desc>
+          <concept_significance>500</concept_significance>
+          </concept>
+      <concept>
+          <concept_id>10002951.10003317.10003347.10003356</concept_id>
+          <concept_desc>Information systems~Clustering and classification</concept_desc>
+          <concept_significance>300</concept_significance>
+          </concept>
+      <concept>
+          <concept_id>10011007.10011074</concept_id>
+          <concept_desc>Software and its engineering~Software creation and management</concept_desc>
+          <concept_significance>300</concept_significance>
+          </concept>
+      <concept>
+          <concept_id>10011007.10011006.10011072</concept_id>
+          <concept_desc>Software and its engineering~Software libraries and repositories</concept_desc>
+          <concept_significance>100</concept_significance>
+          </concept>
+    </ccs2012>
+    \end{CCSXML}
+
+    \ccsdesc[500]{Information systems~Digital libraries and archives}
+    \ccsdesc[300]{Information systems~Clustering and classification}
+    \ccsdesc[300]{Software and its engineering~Software creation and management}
+    \ccsdesc[100]{Software and its engineering~Software libraries and repositories}
 ---
@@
 The models trained include a logistic regression model trained with TF-IDF word embeddings (`tfidf-logit`), a logistic regression model trained with semantic embeddings (`semantic-logit`), and a fine-tuned transformer (`transformer`).
-The semantic embeddings and the base model from which we fine-tuned our own transformer model was the `distilbert-base-uncased-finetuned-sst-2-english` model [@hf_canonical_model_maintainers_2022].
+The semantic embeddings and the base model from which we fine-tuned our own transformer model was the 'distilbert-base-uncased-finetuned-sst-2-english' model [@hf_canonical_model_maintainers_2022].
 Each model was trained with 80% of the NSF-Soft-Search Training dataset.
@@
 
-We wish to thank ....
-
-This work was supported in part by NSF Grant ####
+We thank the USRSSI team, especially Karthik Ram for their input. This material is based upon work supported by the National Science Foundation under Grant 2211275.
 

### 2023-02-14 paper/paper.qmd
Anonymous submission

@@
 author:
-  - name: "Eva Maxfield Brown"
-    email: evamxb@uw.edu
-    orcid: 0000-0003-2564-0373
-    affliation:
-        name: University of Washington Information School
-        city: Seattle
-        state: Washington
-        country: USA
-  - name: "Lindsey Schwartz"
-    email: lsschwar@uw.edu
-    affliation:
-        name: University of Washington Information School
-        city: Seattle
-        state: Washington
-        country: USA
-  - name: "Richard Lewei Huang"
-    email: lwhuang@uw.edu
-    affliation:
-        name: University of Washington Information School
-        city: Seattle
-        state: Washington
-        country: USA
-  - name: "Nicholas Weber"
-    email: nmweber@uw.edu
-    orcid: 0000-0002-6008-3763
-    affliation:
-        name: University of Washington Information School
-        city: Seattle
-        state: Washington
-        country: USA
+  - name: Anonymous Submission
+  # - name: "Eva Maxfield Brown"
+  #   email: evamxb@uw.edu
+  #   orcid: 0000-0003-2564-0373
+  #   affliation:
+  #       name: University of Washington Information School
+  #       city: Seattle
+  #       state: Washington
+  #       country: USA
+  # - name: "Lindsey Schwartz"
+  #   email: lsschwar@uw.edu
+  #   affliation:
+  #       name: University of Washington Information School
+  #       city: Seattle
+  #       state: Washington
+  #       country: USA
+  # - name: "Richard Lewei Huang"
+  #   email: lwhuang@uw.edu
+  #   affliation:
+  #       name: University of Washington Information School
+  #       city: Seattle
+  #       state: Washington
+  #       country: USA
+  # - name: "Nicholas Weber"
+  #   email: nmweber@uw.edu
+  #   orcid: 0000-0002-6008-3763
+  #   affliation:
+  #       name: University of Washington Information School
+  #       city: Seattle
+  #       state: Washington
+  #       country: USA
 
@@
 The result is an inferred dataset of software production for over 150,000 NSF awards.
-We release the NSF-Soft-Search dataset to aid in identifying and understanding research software production: https://github.com/si2-urssi/eager
+We release the NSF-Soft-Search dataset to aid in identifying and understanding research software production: https://github.com/redacted-for-submission
 
@@
 
-The data used for training, and functions to reproduce these models, are made available via our Python package: [`soft-search`](https://github.com/si2-urssi/eager).
+The data used for training, and functions to reproduce these models, are made available via our Python package: [`redacted`](https://github.com/redacted-for-submission).
 
@@
 
-All datasets and predictive models produced by this work are available from our GitHub repository: [`si2-urssi/eager`](https://github.com/si2-urssi/eager).
+All datasets and predictive models produced by this work are available from our GitHub repository: [`redacted`](https://github.com/redacted-for-submission).
 
@@
 
-We thank the USRSSI team, especially Karthik Ram for their input. This material is based upon work supported by the National Science Foundation under Grant 2211275.
+Redacted for anonymous submission.
 

### 2023-02-14 paper/paper.qmd
Update some of the library function names to match paper

@@
 
-from soft_search.data import load_soft_search_2022
+from soft_search.data import load_soft_search_2022_training
 from soft_search.data.soft_search_2022 import SoftSearch2022DatasetFields
@@
 
-soft_search_2022 = load_soft_search_2022()
+soft_search_2022 = load_soft_search_2022_training()
 num_awards_produced_software = len(

### 2023-02-14 soft_search/data/__init__.py

@@ -2,12 +2,15 @@
 
 from pathlib import Path
 
-from .soft_search_2022 import load_soft_search_2022, load_soft_search_2022_irr
+from .soft_search_2022 import (
+    load_soft_search_2022_training,
+    load_soft_search_2022_training_irr,
+)
 
 _DATA_DIR = Path(__file__).parent
 
 __all__ = [
-    "load_soft_search_2022",
-    "load_soft_search_2022_irr",
+    "load_soft_search_2022_training",
+    "load_soft_search_2022_training_irr",
     "_DATA_DIR",
 ]

### 2023-02-14 soft_search/data/irr.py

@@ -7,7 +7,10 @@ from typing import Dict, List, Optional, Union
 import pandas as pd
 from statsmodels.stats.inter_rater import aggregate_raters, fleiss_kappa
 
-from .soft_search_2022 import SoftSearch2022IRRDatasetFields, load_soft_search_2022_irr
+from .soft_search_2022 import (
+    SoftSearch2022IRRDatasetFields,
+    load_soft_search_2022_training_irr,
+)
 
 ###############################################################################
 
@@ -31,7 +34,7 @@ def calc_fleiss_kappa(
 
     See Also
     --------
-    soft_search.data.soft_search_2022.load_soft_search_2022_irr
+    soft_search.data.soft_search_2022.load_soft_search_2022_training_irr
         The function to load the IRR data.
 
     Notes
@@ -95,7 +98,7 @@ def print_irr_summary_stats(  # noqa: C901
         The overall Fliess Kappa statistic.
     """
     # Load IRR data
-    data = load_soft_search_2022_irr()
+    data = load_soft_search_2022_training_irr()
 
     # Sort by link to have consistent order
     sorted_data = data.sort_values(

### 2023-02-14 soft_search/data/soft_search_2022.py

@@ -337,7 +337,7 @@ def _prepare_soft_search_2022(
     return SOFT_SEARCH_2022_DS_PATH
 
 
-def load_soft_search_2022() -> pd.DataFrame:
+def load_soft_search_2022_training() -> pd.DataFrame:
     """
     Load the Software Search 2022 manually labelled dataset.
 
@@ -349,7 +349,7 @@ def load_soft_search_2022() -> pd.DataFrame:
     return pd.read_parquet(SOFT_SEARCH_2022_DS_PATH)
 
 
-def load_soft_search_2022_irr() -> pd.DataFrame:
+def load_soft_search_2022_training_irr() -> pd.DataFrame:
     """
     Load the Software Search 2022 Inter-Rater Reliability labelled dataset.
 

### 2023-02-14 soft_search/label/model_selection.py

@@ -7,7 +7,10 @@ import pandas as pd
 from sklearn.model_selection import train_test_split
 
 from ..data import _DATA_DIR
-from ..data.soft_search_2022 import SoftSearch2022DatasetFields, load_soft_search_2022
+from ..data.soft_search_2022 import (
+    SoftSearch2022DatasetFields,
+    load_soft_search_2022_training,
+)
 from ..seed import set_seed
 from . import regex, semantic_logit, tfidf_logit, transformer
 from .tfidf_logit import (
@@ -30,7 +33,7 @@ def fit_and_eval_all_models(
     set_seed(seed)
 
     # Load core data
-    data = load_soft_search_2022()
+    data = load_soft_search_2022_training()
 
     # Run both models (prediction from abstract and prediction from outcomes)
     results = []

### 2023-02-14 soft_search/label/transformer.py

@@ -245,14 +245,14 @@ def train(
 def _train_and_upload_transformer(seed: int = 0) -> Path:
     import os
 
-    from ..data import load_soft_search_2022
+    from ..data import load_soft_search_2022_training
     from ..seed import set_seed
 
     # Set global seed
     set_seed(seed)
 
     # Load data, train
-    df = load_soft_search_2022()
+    df = load_soft_search_2022_training()
     train_df, test_df = train_test_split(df, test_size=0.2)
     model, _, _, _ = train(
         train_df,

### 2023-02-14 soft_search/tests/label/test_regex.py

@@ -3,7 +3,7 @@
 import pandas as pd
 
 from soft_search.constants import PredictionLabels
-from soft_search.data.soft_search_2022 import load_soft_search_2022
+from soft_search.data.soft_search_2022 import load_soft_search_2022_training
 from soft_search.label import regex
 from soft_search.metrics import EvaluationMetrics
 
@@ -12,7 +12,7 @@ from soft_search.metrics import EvaluationMetrics
 
 def test_regex_train() -> None:
     # Load data (and sample for fast tests)
-    data = load_soft_search_2022().sample(n=40)
+    data = load_soft_search_2022_training().sample(n=40)
 
     # "Train" and get eval metrics
     metrics = regex.train(data)

### 2023-02-14 soft_search/tests/label/test_semantic_logit.py

@@ -5,7 +5,7 @@ from sklearn.pipeline import Pipeline
 
 from soft_search.data.soft_search_2022 import (
     SoftSearch2022DatasetFields,
-    load_soft_search_2022,
+    load_soft_search_2022_training,
 )
 from soft_search.label import semantic_logit
 from soft_search.metrics import EvaluationMetrics
@@ -15,7 +15,7 @@ from soft_search.metrics import EvaluationMetrics
 
 def test_semantic_logit_train() -> None:
     # Load data (and sample for fast tests)
-    data = load_soft_search_2022().sample(n=40)
+    data = load_soft_search_2022_training().sample(n=40)
 
     # Split
     train_df, test_df = train_test_split(

### 2023-02-14 soft_search/tests/label/test_tfidf_logit.py

@@ -5,7 +5,7 @@ from sklearn.pipeline import Pipeline
 
 from soft_search.data.soft_search_2022 import (
     SoftSearch2022DatasetFields,
-    load_soft_search_2022,
+    load_soft_search_2022_training,
 )
 from soft_search.label import tfidf_logit
 from soft_search.metrics import EvaluationMetrics
@@ -15,7 +15,7 @@ from soft_search.metrics import EvaluationMetrics
 
 def test_tfidf_logit_train() -> None:
     # Load data (and sample for fast tests)
-    data = load_soft_search_2022().sample(n=40)
+    data = load_soft_search_2022_training().sample(n=40)
 
     # Split
     train_df, test_df = train_test_split(

### 2023-02-14 docs/conf.py
Include web version of paper

@@ -92,7 +92,7 @@ release = soft_search.__version__
 #
 # This is also used if you do content translation via gettext catalogs.
 # Usually you set "language" from the command line for these cases.
-language = None
+language = "en"
 
 # List of patterns, relative to source directory, that match files and
 # directories to ignore when looking for source files.

### 2023-02-18 paper/paper.qmd
Update paper after title change

--- 2023-02-14 paper/paper.qmd
@@
 ---
-title: "Searching for Software in NSF Awards"
+title: "NSF-Soft-Search: Two Datasets to Study the Identification and Production of Research Software"
 author:
+  # - name: Anonymous Submission
   - name: "Eva Maxfield Brown"
@@
   # comment this out to make submission anonymous
-  anonymous: true
+  # anonymous: true
 

### 2023-02-27 paper/paper.qmd
arXiv paper submission (had to port to Overleaf)

@@
 ---
-title: "NSF-Soft-Search: Two Datasets to Study the Identification and Production of Research Software"
+title: "Soft-Search: Two Datasets to Study the Identification and Production of Research Software"
 author:
-  # - name: Anonymous Submission
   - name: "Eva Maxfield Brown"
@@
     email: lsschwar@uw.edu
+    orcid: 0000-0001-8338-0288
     affliation:
@@
     email: lwhuang@uw.edu
+    orcid: 0000-0002-0264-9300
     affliation:
@@
 The result is an inferred dataset of software production for over 150,000 NSF awards.
-We release the NSF-Soft-Search dataset to aid in identifying and understanding research software production: https://github.com/si2-urssi/eager
+We release the Soft-Search dataset to aid in identifying and understanding research software production: https://github.com/si2-urssi/eager
 
@@
   # comment this out to specify detailed document options
-  acmart-options: sigconf
+  acmart-options: sigconf, review
 
@@
   conference-location: Santa Fe, NM
-  # price: "15.00"
-  # isbn: 978-1-4503-XXXX-X/18/06
+  price: "15.00"
+  isbn: 978-1-4503-XXXX-X/18/06
 
   # if present, replaces the list of authors in the page header.
-  shortauthors: Brown et al.
+  # shortauthors: Brown et al.
 
@@
 However, records of software production are not readily identifiable or available at scale in the way that peer-reviewed publications or other scholarly outputs are [@Schindler2022TheRO].
-To make progress on this problem, we introduce two related datasets for studying and inferring software produced as a part of research, which we refer to as the NSF-Soft-Search dataset.
+To make progress on this problem, we introduce two related datasets for studying and inferring software produced as a part of research, which we refer to as the Soft-Search dataset.
 
-The NSF-Soft-Search dataset is aimed at identifying research projects which are likely to have produced software while funded by a federal grant.
+The Soft-Search dataset is aimed at identifying research projects which are likely to have produced software while funded by a federal grant.
 We start by identifying GitHub repositories that  acknowledge funding from at least one National Science Foundation (NSF) award.
@@
 We then link each annotated GitHub repository to the specific NSF award ID(s) referenced in its README.md file.
-Finally, we compile the NSF-Soft-Search Training dataset using the annotations for each GitHub repository, and the text from the linked NSF award abstract and the project outcomes report.
+Finally, we compile the Soft-Search Training dataset using the annotations for each GitHub repository, and the text from the linked NSF award abstract and the project outcomes report.
 
-Using the NSF-Soft-Search Training dataset, we train a variety of models to predict software production using either the NSF award abstract or project outcomes report text as input.
+Using the Soft-Search Training dataset, we train a variety of models to predict software production using either the NSF award abstract or project outcomes report text as input.
 We use the best performing models to then infer software production against all awards funded by the National Science Foundation from 2010 to 2023 (additional details are offered in @sec-data-collection).
-The predictions and metadata for each NSF award between the 2010 and 2023 period are compiled to form the NSF-Soft-Search Inferred dataset.
+The predictions and metadata for each NSF award between the 2010 and 2023 period are compiled to form the Soft-Search Inferred dataset.
 
-In total, our new NSF-Soft-Search dataset includes the following contributions:
+In total, our new Soft-Search dataset includes the following contributions:
 
-1. NSF-Soft-Search Training: A ground truth dataset compiled using linked NSF awards and GitHub repositories which have been annotated for software production.
+1. Soft-Search Training: A ground truth dataset compiled using linked NSF awards and GitHub repositories which have been annotated for software production.
 2. Multiple classifiers which infer software production from either the text of an NSF award’s abstract or project outcomes report.
 3.
-NSF-Soft-Search Inferred: A dataset of more than 150,000 NSF funded awards from between 2010 and 2023.
+Soft-Search Inferred: A dataset of more than 150,000 NSF funded awards from between 2010 and 2023.
 Each award has two predictions for software production: one from prediction using the abstract text and the other from prediction using the project outcomes report text.
@@
 The rest of the paper proceeds as follows.
-In @sec-data-collection we detail the data collection and annotation process used for creating the NSF-Soft-Search Training dataset.
+In @sec-data-collection we detail the data collection and annotation process used for creating the Soft-Search Training dataset.
 In @sec-models we briefly describe the model training process and report results.
-In @sec-nsf-soft-search-dataset we provide summary statistics for the NSF-Soft-Search Inferred dataset and observe trends in software production over time.
+In @sec-soft-search-dataset we provide summary statistics for the Soft-Search Inferred dataset and observe trends in software production over time.
 We conclude with discussion regarding the limitations of our approach and opportunities for future work.
@@
 
-Using the compiled NSF-Soft-Search Training dataset, we trained three different models using the text from either the award abstract or project outcomes report.
+Using the compiled Soft-Search Training dataset, we trained three different models using the text from either the award abstract or project outcomes report.
 The models trained include a logistic regression model trained with TF-IDF word embeddings (`tfidf-logit`), a logistic regression model trained with semantic embeddings (`semantic-logit`), and a fine-tuned transformer (`transformer`).
 The semantic embeddings and the base model from which we fine-tuned our own transformer model was the 'distilbert-base-uncased-finetuned-sst-2-english' model [@hf_canonical_model_maintainers_2022].
-Each model was trained with 80% of the NSF-Soft-Search Training dataset.
+Each model was trained with 80% of the Soft-Search Training dataset.
 We then test each of the models and use F1 to rank each model’s performance.
@@
 
-model_results = fit_and_eval_all_models().round(3)
+model_results = fit_and_eval_all_models(train_transformer=True).round(3)
 ```
@@
 
-# The NSF-Soft-Search Dataset {#sec-nsf-soft-search-dataset}
+# The Soft-Search Dataset {#sec-soft-search-dataset}
 
-Using the predictive models, we compile the NSF-Soft-Search Inferred dataset which contains the metadata, abstract text, and project outcomes report text, for all NSF awarded projects during the 2010-2023 period.
-The NSF-Soft-Search Inferred dataset additionally contains our predictions for software production using both texts respectively.
+Using the predictive models, we compile the Soft-Search Inferred dataset which contains the metadata, abstract text, and project outcomes report text, for all NSF awarded projects during the 2010-2023 period.
+The Soft-Search Inferred dataset additionally contains our predictions for software production using both texts respectively.
 
@@
 #| warning: false
-#| label: tbl-nsf-soft-search-stats
+#| label: tbl-soft-search-stats
 #| tbl-cap: Composition of the NSF Soft Search Dataset
@@
 
-Using the NSF-Soft-Search Inferred dataset we can observe trends in software production over time.
+Using the Soft-Search Inferred dataset we can observe trends in software production over time.
 @fig-soft-over-time plots the percent of awards which we predict to have produced software (using the award's abstract) over time.
@@
 
-We introduce NSF-Soft-Search, a pair of novel datasets for studying software production from NSF funded projects.
-The NSF-Soft-Search Training dataset is a human-labeled dataset with almost 1000 examples used to train models which predict software production from either the NSF award abstract text or the project outcomes report text.
-We used these models to generate the NSF-Soft-Search Inferred dataset.
-The NSF-Soft-Search Inferred dataset includes project metadata, the awards abstract and project outcomes report, and predictions of software production for each NSF funded project between 2010 and 2023.
-We hope that NSF-Soft-Search helps further new studies and findings in understanding the role software development plays in scholarly publication.
+We introduce Soft-Search, a pair of novel datasets for studying software production from NSF funded projects.
+The Soft-Search Training dataset is a human-labeled dataset with almost 1000 examples used to train models which predict software production from either the NSF award abstract text or the project outcomes report text.
+We used these models to generate the Soft-Search Inferred dataset.
+The Soft-Search Inferred dataset includes project metadata, the awards abstract and project outcomes report, and predictions of software production for each NSF funded project between 2010 and 2023.
+We hope that Soft-Search helps further new studies and findings in understanding the role software development plays in scholarly publication.
 
@@
 
-As discussed in @sec-data-collection, the NSF-Soft-Search Training dataset was entirely composed of NSF awards which ultimately released or hosted software (and other research products) on GitHub.
+As discussed in @sec-data-collection, the Soft-Search Training dataset was entirely composed of NSF awards which ultimately released or hosted software (and other research products) on GitHub.
 Due to our data collection strategy, it is possible that each of the predictive models learned not to predict if an NSF award would produce software, but rather, if an NSF award would produce software hosted on GitHub.
